Supplemental Appendix for ``An asymptotically normal out-of-sample test of equal predictive accuracy for nested models''

### 2014-11-03 appendix.tex
Tweak notation
Add proof of vcv consistency

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
  \end{equation*}
  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
  we can rewrite this summation as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.

@@

\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
\begin{proof}
  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
  \citet{RoW:05} complete the proof.
\end{proof}

>>>>

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation*}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
  \end{equation*}
  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
  we can rewrite this summation as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.

@@

\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
We will only prove $\Sigmah_2 \to^p \Sigma$. The result for
$\Sigmah_1$ is essentially the same, but uses \citet{JoD:00} instead
of the simple \lln.
\begin{proof}
  First
  \begin{align*}
    \Sh_{21} &= \oavg{t} (f_t - \E \fb(\btrue) + \fh_t - f_t - \fb + \E \fb(\btrue))^2 \\
    \Sh_{22} &= \oavg{t} (f_t - \E \fb(\btrue) + \fh_t - f_t - \fb + \E \fb(\btrue))
                        (g_t - \E \gb^* + \gh_t - g_t - \gb + \E \gb^*)
    \intertext{and}
    \Sh_{23} &= \oavg{t} (g_t - \E \gb^* + \gh_t - g_t - \gb + \E \gb^*)^2
  \end{align*}
  so $\Sigmah_2 \to^p \Sigma$ as long as
  $\fb - \E \fb(\btrue) \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E \fb^*)^2 \to^p \var(\sqrt{P} \fb^*) \label{eq:1} \\
    \oavg{t} (g_t - \E \gb^*)^2 \to^p \var(\sqrt{P} \gb^*) \label{eq:3} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
  \end{gather}
  The first two results are proven in Theorem~\ref{res:1}
  and~\eqref{eq:1} and~\eqref{eq:3} follow from the \lln, so it
  suffices to prove~\eqref{eq:4} and~\eqref{eq:5}.

  As before, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Some algebra reveals
  that~\eqref{eq:4} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \label{eq:14}.
  \end{gather}
  Now~\eqref{eq:10} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \sup_{t=R+1,\dots,R'} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \sup_{t=R'+1,\dots,T} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big) (2 x_t'\btrue - y_{t+1} - \yh_{t+1}) \\
    &\leq \sup_{t=R+1,\dots,R'} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \sup_{t=R'+1,\dots,T} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero by construction. The proof of~\eqref{eq:5} is similar.
\end{proof}
